### 2018-08-17 README.Rmd
compare with 2006 not 2011 nlcd

lg_ep <- mutate(lg$iws.lulc, 
                lg_ag = rowSums(cbind(iws_nlcd2011_pct_81, 
                                      iws_nlcd2011_pct_82), na.rm = TRUE)) %>%
  select(lagoslakeid, lg_ag) %>%
  left_join(ep, by = "lagoslakeid") %>%
  filter(!is.na(tp))

@@

plot_grid(
ggplot() +
  geom_point(data = lg_ep, aes(x = lg_ag, y = tp)) +
  xlab("LAGOS (NLCD 2011) Ag (%)"),
ggplot() +
  geom_point(data = cdl_ep, aes(x = cdl_ag, y = tp)) +
  xlab("CDL Ag (%)"),
ggplot() + 
  geom_point(data = usgs_ep, aes(x = phosphorus_input, y = tp)) + 
  scale_x_log10() + 
  xlab("log(P Input)"))

>>>>

lg_ep <- mutate(lg$iws.lulc, 
                lg_ag = rowSums(cbind(iws_nlcd2006_pct_81, 
                                      iws_nlcd2006_pct_82), na.rm = TRUE)) %>%
  select(lagoslakeid, lg_ag) %>%
  left_join(ep, by = "lagoslakeid") %>%
  filter(!is.na(tp))

@@

plot_grid(
ggplot() +
  geom_point(data = lg_ep, aes(x = lg_ag, y = tp)) +
  xlab("LAGOS (NLCD 2006) Ag (%)"),
ggplot() +
  geom_point(data = cdl_ep, aes(x = cdl_ag, y = tp)) +
  xlab("CDL Ag (%)"),
ggplot() + 
  geom_point(data = usgs_ep, aes(x = phosphorus_input, y = tp)) + 
  scale_x_log10() + 
  xlab("log(P Input)"))
